---
title: "2101116096-MAS6024(1).Rmd"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part 1

## Set the lgrid and green square

```{r echo=TRUE}
lgrid <- matrix(NA, nrow = 8, ncol = 8)
lgrid[1,] <- c("r", "l", "q", "s", "t", "z", "c", "a")
lgrid[2,] <- c("i", "v", "d", "z", "h", "l", "t", "p")
lgrid[3,] <- c("u", "r", "o", "y", "w", "c", "a", "c")
lgrid[4,] <- c("x", "r", "f", "n", "d", "p", "g", "v")
lgrid[5,] <- c("h", "j", "f", "f", "k", "h", "g", "m")
lgrid[6,] <- c("k", "y", "e", "x", "x", "g", "k", "i")
lgrid[7,] <- c("l", "q", "e", "q", "f", "u", "e", "b")
lgrid[8,] <- c("l", "s", "d", "h", "i", "k", "y", "n")
# ======================================================= #
green_squares <- matrix(NA, nrow = 4, ncol = 2)
green_squares[1,] <- c(2,6)
green_squares[2,] <- c(3,7)
green_squares[3,] <- c(6,2)
green_squares[4,] <- c(7,3)
```

## assign basic movement rules

```{r}
moves <- function(current_square){
  i <- current_square[1]
  j <- current_square[2]
  #judge whether current square is at the edge of the board
  if(i==1 | j==1 | i==8 | j == 8){# if at the edge of the board,make a randomly move.
    current_square <- c(sample(1:8,1),sample(1:8,1))
    # select a random square from 64 squares, include do not make movement.
    return(current_square)
  #if not at the edage of the board, make a move to one adjacent square.
  }else{
    #assign coordinate change variables，horizontal coordinates=hc; vertical coordinate=vc
    hc=0
    vc=0
    # exclude no movement 
    while(hc==0 & vc == 0){
    hc <- seq(-1,1,1)[sample(1:3,1)]
    vc <- seq(-1,1,1)[sample(1:3,1)]
    }
    current_square <- c(i+hc,j+vc)
    return(current_square)
  }
}
```

## assign the rule when landed on the green square

```{r}
green_moves <- function(lgrid, current_square, p, letters_list, green_squares, add){
  current_letter <- lgrid[current_square[1], current_square[2]]
  # assign the random probability
  random_green_probaility <- runif(1,0,1)
  landed_at_greensquares <- c()
  # test if moved to the green square
  for(i in seq(1:dim(green_squares)[1])){
    landed_at_greensquares <- append(landed_at_greensquares, all(current_square == green_squares[i,]))
  }
  # if the square move to one of the green squares, then judge landed on which green square.
  if(any(landed_at_greensquares)){
    greensquares_numbers<- which(current_square[1] == green_squares[,1])
  # judge next turn use which rule of tow rules, 
  #  depend on the random random_green_probability compare with the given probability
    if (random_green_probaility < p){
      letters_list <- c('f','f','h','k') 
    # if random_green_probaility < p, replace the letters list with (f,f,h,k)
    }else{
          remove_letter_coordinates <- green_squares[greensquares_numbers,]
          remove_letter <- lgrid[remove_letter_coordinates[1],
                                 remove_letter_coordinates[2]]
      letters_list <- letters_list[letters_list != remove_letter]# remove all same copies.
    }
  }else{ # if not at green squares.
    if(add==TRUE){
      letters_list <- append(letters_list, current_letter)
    }else {
      letters_list <- letters_list#
    }
   }
  return(letters_list)
}
```

### Part 2

## set the strategy to finish the game in the fewest possible turns

```{r}


#### Define strategy
strategy <- function(current_square,letters_list,lgrid){
  add <- TRUE
  not_add <- FALSE
  number_of_list <- length(letters_list)
  letters_list_data <- as.data.frame(sort((table(letters_list))))#The number of letters has been collected
  lgrid_list_data <- as.data.frame(sort(table(lgrid)))#Count all letters
  current_letter <- lgrid[current_square[1], current_square[2]]
  #Determines whether a letter appears in the list of collected letters
  current_letter_exit <- is.element(current_letter,letters_list_data[,1])
  if(number_of_list < 3){ # if letter list less than 3 letters
    letters_freq_all <- lgrid_list_data[which(current_letter == lgrid_list_data), 2]
    #Determine if the letter appears more than twice in all squares
    if(letters_freq_all >= 2){ 
      return(add)
     }else{
      return(not_add)
       }
  }else if(number_of_list ==3){ # Rule to add the 4th letter
   # If there are three different letters in the collected letter list, 
   # the current letter is same with anyone of these three letters, add this letter to the collected letter list. 
   if(dim(letters_list_data)[1] == 3 & current_letter_exit == TRUE){
     return(add)
   }else{
   # If there are two different letters in the collected letter list, or only the same letters, you can choose to add.
     if(dim(letters_list_data)[1] == 2 | dim(letters_list_data)[1] == 1){
       return(add)
     }else{
       return(not_add)
     }
   }
  }else if(number_of_list == 4){ # Rule to add the 5th letter
    #If there are three different letters  in the collected letter list, select the letter whose occurrence is one to add.
    if(dim(letters_list_data)[1] == 3 & current_letter_exit ==TRUE){
      one_time_letter <- is.element(current_letter,letters_list_data[1:2,1])
        if(one_time_letter == TRUE){
          return(add)
        }
    # If there are two different letters in the collected letter list, add this letter directly.
      }else if(dim(letters_list_data)[1] == 2 & current_letter_exit ==TRUE){
        return(add)
        }
    }else{#If all letters in the collected letter list are the same, add it directly.
      return(add)
    }
  return(not_add)
}
```

It identifies three situations in the collected letter list where the number of letters is less than 3, equal to 3 and equal to 4. Then decide whether to add the letter in the current box according to the three different frequencies that can appear in the letter list. The three frequencies are divided into three different letters, two different letters and all the same letters. According to this strategy, palindrome letter lists can be obtained in relatively few turns. ##\# Part 3
### Part 3
```{r}
begin_game <- function(lgrid, green_squares, initial_position, p){
  turn <- 0
  letters_list <-c()
  current_square <-c()
  current_square <- initial_position
  i <- current_square[1]
  j <- current_square[2]
  begin_condition <- i !=1&8 & j!=1&8
   while (begin_condition == TRUE){
    add <- strategy(current_square,letters_list, lgrid)
    letters_list <- green_moves(lgrid, current_square, p, letters_list, green_squares, add)
    current_square <- moves(current_square)
    current_letter <- lgrid[current_square[1], current_square[2]]
    if(length(letters_list) > 5){
      begin_condition <- FALSE
    }
    turn <- turn + 1
  }
  return(turn)
}
```

### Part 4

```{r}
library(tidyverse)
mean_D4_turn <-c()
for(i in seq(0,1,0.02)){
  for (j in seq(1:10)) {
  sum_turn_D4 <- 0
   turn <- begin_game(lgrid, green_squares, c(4,4), i )
  sum_turn_D4 <- turn + sum_turn_D4
  }
  mean_D4_turn <- append(mean_D4_turn,sum_turn_D4/10)
}
probability <- c(seq(0:50)) 
average_D4 = data.frame(probability,mean_D4_turn)
ggplot(data=average_D4, aes(x = probability, y = mean_D4_turn)) +
                  geom_point()+
                  labs(x="Probability",y="Mean of D4 sum turns")
                  
                  
```

As you can see from this scatter chart, there is no significant effect between the average number of turns required to complete the game and the probability


### Part 5

```{r warning=FALSE}
### D4 0.95
all_turn_D4 <- c()
for(i in seq(1:100)){
  turn <- begin_game(lgrid, green_squares, c(4,4), 0.95)
  all_turn_D4 <- append(all_turn_D4,turn)
}

### F6 0.05
all_turn_F6 <- c()
for(i in seq(1:100)){
  turn <- begin_game(lgrid, green_squares, c(6,6), 0.05)
  all_turn_F6 <- append(all_turn_F6,turn)
}
D4<-as.data.frame(table(all_turn_D4))
F6<-as.data.frame(table(all_turn_F6))
ggplot(data=D4, aes(x = all_turn_D4, y = Freq)) +
                  geom_point()+
                  labs(x="all_D4_turns",y="Freq")
```
```{r}
ggplot(data=F6, aes(x = all_turn_F6, y = Freq)) +
                  geom_point()+
                  labs(x="all_F6_turns",y="Freq")

```

As can be seen from the two bar charts, the number of rounds required to complete the game from D4 and F6 varies roughly the same. The probability of completing a larger number of turns is low.
### Part 6

```{r}
XA<-c(25, 13, 16, 24, 11, 12, 24, 26, 15, 19, 34)
XB<-c(35, 41, 23, 26, 18, 15, 33, 42, 18, 47, 21, 26)
t.test(XA,XB,paired = FALSE)
```
As the P-value = 0.02968 < 0.05,There is A difference between the samples of total turns from square A and square B, so EA is not equal to EB.